Trait pleiotropy of regulatory variants increases with the variety of bound transcription factors, regulated genes and active tissues

### 2022-08-28 ms/ms02_intro.tex
ENH beta and pval improvements

The large number of GWAS has allowed to discover that many genetic variants are involved in different traits \citep{2019.Posthuma.Watanabe}.
%
In this work, the analysed loci covered 60\% of the genome and 90\% of these loci contained associations across different traits \citep{2019.Posthuma.Watanabe}.
%
They also found that pleiotropic genes and variants where less tissue specific in terms of gene expression and eQTLs \citep{2019.Posthuma.Watanabe}.
%
The question of tissue specificity of eQTLs has been analyzed in different works with conflicting conclusions \citep{2021.Li.Mu.GenomeBiology.impactcelltype,2018.Vijayanand.Schmiedel.Cell.ImpactGeneticPolymorphisms,2017...Nature.Geneticeffectsgene}.

>>>>

The large number of GWAS has allowed to discover that many genetic variants are involved in different traits \citep{2019.Posthuma.Watanabe}.
%
In this work, the analysed loci covered 60\% of the genome and 90\% of these loci contained associations across different traits \citep{2019.Posthuma.Watanabe}.
%
They also found that pleiotropic genes and variants where less tissue specific in terms of gene expression and eQTLs \citep{2019.Posthuma.Watanabe}.
%
The question of tissue specificity of eQTLs has been analyzed in different works with conflicting conclusions \citep{2021.Li.Mu.GenomeBiology.impactcelltype,2018.Vijayanand.Schmiedel.Cell.ImpactGeneticPolymorphisms,2017...Nature}.

### 2022-08-28 ms/ms03_results.tex
ENH beta and pval improvements

% 12q24.12
For instance, the most pleiotropic variants in cytoband 12q24.12 are involved in allergies, cancer, cardiovascular and autoimmune diseases (Table \ref{tab:pleitropic_variants}).
%
These variants control egenes ALDH2, LINC01405, MAPKAPK5, SH2B3 that are involved in alcohol-related disorders (ALDH2), cancer (LINC01405), multiple congenital anomalies syndromes (MAPKAPK5),  inflammation and hematological disorders (SH2B3).
%
These eQTLs are active in adipose tissue, arteries, blood, colon, immune cells, skin and induced pluripotent stem cells (iPSC).

@@

Then I evaluated the function of pleiotropic variants with 5, 4, 3 and 2 GWAS categories using gene ontology analysis.
%
I analyzed the ontology of egenes with 5, 4, 3 and 2 GWAS categories using the DAVID web services \citep{2008.Lempicki.Huang,2008.Lempicki.Huang.NucleicAcidsResearch}.
%
I found that egenes of pleiotropic variants with 3 and 2 GWAS categories were significantly enriched in functions of the immune system (Fig. \ref{s:results}{fig:geneontology}).
For instance, egenes in the cytoband 5q31.1 include IRF1 and IL4, which are important factors of the immune system.
%
IRF1 is a response protein to the presence of virus and oncogenic proteins and IL4 is required to stimulate proliferation of activated B and T-cells.
%
Variant rs17622656 is located in the intron of the IRF1 gene whereas variants rs736801 and rs2522051 are located upstream and downstream of the IRF1 gene, respectively.
%
These variants are associated with allergy, asthma, cardiovascular diseases, hypertension and ulcerative colitis and are active in a large number of tissues such as arteries, blood, brain, breast, digestive and immune system, muscle, skin, ovary, testis and thyroid.

%Variants of the 3q23 cytoband are involved in allergy, cancer and height traits (Supplementary table 3).
%%
%Interestingly all these variants target the egene ZBTB3.
%%
%ZBTB3 is a transcription factor that controls pro-inflammatory factors such as IRF5 (10.1016/j.jaut.2016.08.001).
%%
%These variants are active in tissues such as blood, esophagus, immune cell, LCLs and muscle (Supplementary table 3).

%%11q13.5
%The variants in cytoband 11q13.5 are involved in allergy and autoimmune disease (Supplementary table 3).
%%
%All these variants target the egene EMSY-DT, which is a long noncoding RNA upstream of EMSY.
%%
%These variants are active in LCL, Skin and iPSC (Supplementary table 3).
%
%In summary, I have identified pleiotropic variants with gene regulatory function.
%%
%Some of these loci are strongly involved in the immune system.

@@

\subsection*{How specific are variants to GWAS traits, egenes and etissues?}

Next I explored the trait, egene and etissue specificity of eQTL/GWAS variants.
%
83\% of variants are involved in one GWAS category, 14\% are involved in 2 categories and the remaining variants with 3 or more trait categories make 3\% or less (Fig. \ref{fig:hist_gwas_egene_etissue}(a).
%
Regarding egenes, half of variants modulate one egene, and the other half modulate two or more egenes (Fig. \ref{fig:hist_gwas_egene_etissue}(b).
%
In the case of etissues, only 40\% of variants are specific to a single tissue while the other 60\% are active in two or more tissues (Fig. \ref{fig:hist_gwas_egene_etissue}(c).
%
In conclusion, most colocalized eQTL/GWAS variants are specific to one GWAS trait. By contrast, half of them only module one specific egene, and less than half are active in a single tissue.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{How do trait frequencies relates to eQTL and etissue frequency at the loci level?}

In Figure \ref{fig:region_gwas_egenes_tissues}, I have plotted the number of GWAS categories, egenes and eTissues for regulatory variants in three pleiotropic regions.
%
All three regions are very pleiotropic with very different associated trait categories such as cancer, cardiovascular and autoimmune diseases.
%
However these plots show that the relationship between the number of traits, egenes and etissues can be very different.
%
The SLC22A5 locus in region 5:132,239,645-132,497,907 (5q31.1) has a low number of egenes but a high number of etissues.
%
By contrast, the MHC locus in region 6:31,034,839-32,478,149 (6p21.33) has a high number of both egenes and etissues.
%
Finally, the ATXN2 locus in region 12:111,395,984-111,645,358 (12q24.12) shows the highest trait pleiotropy but the number of egenes and etissues is very low.
%
In summary, trait pleiotropy can arise from different situations: few egenes and etissues, many egenes and etissues or a mix of both.

@@

Then, I wanted to understand the molecular mechanism of pleiotropic regions.

@@

I first analysed whether there are significant differences of effect consequences between more and less pleiotropic variants.
%
I separated variants according to the count of GWAS categories and computed the EBI variant effect predictor (VEP) consequence \citep{2016.Cunningham.McLaren}.
%
I found a significant increase of missense variants among variants with 2, 3 and 4 categories compared to variants with 1 category (Fig. \ref{fig:vep_consequence}a).
%
I also found a significant increase of splicing variants among variants with 3 categories (Fig. \ref{fig:vep_consequence}b).
%
Finally, there is also a significant increase of the 3'-UTR variants among variants with 4 categories (Fig. \ref{fig:vep_consequence}c).
%
These analyses suggest that more pleiotropic variants have a stronger effect on the coding sequence and splicing regions, which might explain partly their more pleiotropic function.

\subsubsection*{More egenes per variant-etissue?}

Then I hypothesized that pleiotropic variant-etissue pairs modulate more egenes.
%
I found that pleiotropic variant-etissues pairs have significantly more egenes compared to variants with one GWAS category (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
This observation could be explained by my previous observation that pleiotropic variants have more often an effect on the splicing and 3'UTR regions (Figure \ref{fig:vep_consequence}b,c).

\subsubsection*{More etissues per variant-egene?}

My next hypothesis was that pleiotropic variant-egene pairs are active in more tissues compared with variant-egene pairs with one GWAS category and this increases their probability to affect more GWAS categories.
%
Indeed, I found that pleiotropic variant-egenes pairs are associated with a higher number of etissues (Fig. \ref{fig:gwas_egene_etisue_per_variant}b).

@@

I hypothesized that pleiotropic variants are active in more etissues, because genomic regions around pleiotropic variants bind more transcription factors, which upregulate the pleiotropic regions in more tissues.
%
I looked at the number of unique transcription factors bound in a window of 100 bp around each variant.
%
I found a significant increase of unique transcription factors around pleagonzaleziotropic variants (Fig. \ref{fig:freq_tf_per_variant}a).

\subsubsection*{More GWAS per variant-egene-etissue?}

Another molecular mechanism of pleiotropy is that egenes correlate with more GWAS categories even after taking into account variants and etissues.
%
I computed the number of GWAS categories per variant-egene-etissue triplet.
%
Indeed I found a significant increase of GWAS categories for pleiotropic variant-egene-etissue triplets (Fig. \ref{fig:gwas_egene_etisue_per_variant}c).
%
This observation could be explained by my previous observation that pleiotropic variants have more often missense effects (Fig. \ref{fig:vep_consequence}a).

\subsection*{What is the effect size of pleiotropic eQTLs?}

Then I wondered, how does the effect size (beta) and significance (p-value) relate to pleiotropy.
%
I found a significant decrease of effect size of eQTLs and GWAS variants with the exception of the GWAS effect size of variants with 3 categories (Fig. \ref{fig:beta_pval}a,b).

Then I looked at the significance of pleiotropic eQTLs and GWAS variants.
%
eQTL significance significantly decreased for pleiotropic variants (Fig. \ref{fig:beta_pval}c).
%
By contrast, the significance of GWAS associations increased for GWAS variants (Fig. \ref{fig:beta_pval}d).

In summary, pleiotropic eQTLs are weaker with a weaker beta and less significant p-values..
%
On the other hand, the effect size of GWAS seems smaller for pleiotropic variants but the significance is stronger.

>>>>

% 12q24.12
For instance, the most pleiotropic variants in cytoband 12q24.12 are involved in allergies, cancer, cardiovascular and autoimmune diseases (Table \ref{tab:pleitropic_variants}).
%
These variants control eGenes ALDH2, LINC01405, MAPKAPK5, SH2B3 that are involved in alcohol-related disorders (ALDH2), cancer (LINC01405), multiple congenital anomalies syndromes (MAPKAPK5),  inflammation and hematological disorders (SH2B3).
%
These eQTLs are active in adipose tissue, arteries, blood, colon, immune cells, skin and induced pluripotent stem cells (iPSC).

@@

Then I evaluated the function of pleiotropic variants with 5, 4, 3 and 2 GWAS categories using gene ontology analysis.
%
I analyzed the ontology of eGenes with 5, 4, 3 and 2 GWAS categories using the DAVID web services \citep{2008.Lempicki.Huang,2008.Lempicki.Huang.NucleicAcidsResearch}.
%
I found that eGenes of pleiotropic variants with 3 and 2 GWAS categories were significantly enriched in functions of the immune system (Fig. \ref{s:results}{fig:geneontology}).
For instance, eGenes in the cytoband 5q31.1 include IRF1 and IL4, which are important factors of the immune system.
%
IRF1 is a response protein to the presence of virus and oncogenic proteins and IL4 is required to stimulate proliferation of activated B and T-cells.
%
Variant rs17622656 is located in the intron of the IRF1 gene whereas variants rs736801 and rs2522051 are located upstream and downstream of the IRF1 gene, respectively.
%
These variants are associated with allergy, asthma, cardiovascular diseases, hypertension and ulcerative colitis and are active in a large number of tissues such as arteries, blood, brain, breast, digestive and immune system, muscle, skin, ovary, testis and thyroid.

%Variants of the 3q23 cytoband are involved in allergy, cancer and height traits (Supplementary table 3).
%%
%Interestingly all these variants target the eGene ZBTB3.
%%
%ZBTB3 is a transcription factor that controls pro-inflammatory factors such as IRF5 (10.1016/j.jaut.2016.08.001).
%%
%These variants are active in tissues such as blood, esophagus, immune cell, LCLs and muscle (Supplementary table 3).

%%11q13.5
%The variants in cytoband 11q13.5 are involved in allergy and autoimmune disease (Supplementary table 3).
%%
%All these variants target the eGene EMSY-DT, which is a long noncoding RNA upstream of EMSY.
%%
%These variants are active in LCL, Skin and iPSC (Supplementary table 3).
%
%In summary, I have identified pleiotropic variants with gene regulatory function.
%%
%Some of these loci are strongly involved in the immune system.

@@

\subsection*{How specific are variants to GWAS traits, eGenes and eTissues?}

Next I explored the trait, eGene and eTissue specificity of eQTL/GWAS variants.
%
83\% of variants are involved in one GWAS category, 14\% are involved in 2 categories and the remaining variants with 3 or more trait categories make 3\% or less (Fig. \ref{fig:hist_gwas_egene_etissue}(a).
%
Regarding eGenes, half of variants modulate one eGene, and the other half modulate two or more eGenes (Fig. \ref{fig:hist_gwas_egene_etissue}(b).
%
In the case of eTissues, only 40\% of variants are specific to a single tissue while the other 60\% are active in two or more tissues (Fig. \ref{fig:hist_gwas_egene_etissue}(c).
%
In conclusion, most colocalized eQTL/GWAS variants are specific to one GWAS trait. By contrast, half of them only module one specific eGene, and less than half are active in a single tissue.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{How do trait frequencies relates to eQTL and eTissue frequency at the loci level?}

In Figure \ref{fig:region_gwas_egenes_tissues}, I have plotted the number of GWAS categories, eGenes and eTissues for regulatory variants in three pleiotropic regions.
%
All three regions are very pleiotropic with very different associated trait categories such as cancer, cardiovascular and autoimmune diseases.
%
However these plots show that the relationship between the number of traits, eGenes and eTissues can be very different.
%
The SLC22A5 locus in region 5:132,239,645-132,497,907 (5q31.1) has a low number of eGenes but a high number of eTissues.
%
By contrast, the MHC locus in region 6:31,034,839-32,478,149 (6p21.33) has a high number of both eGenes and eTissues.
%
Finally, the ATXN2 locus in region 12:111,395,984-111,645,358 (12q24.12) shows the highest trait pleiotropy but the number of eGenes and eTissues is very low.
%
In summary, trait pleiotropy can arise from different situations: few eGenes and eTissues, many eGenes and eTissues or a mix of both.

@@

Then, I wanted to understand the molecular mechanism of pleiotropic variants and regions.
%
I hypothesized that pleiotropy arises from bias in regulatory effects of variants.
%
For instance, pleiotropic variants might significantly affect some molecular functions more often.
%
Another possibility is that pleiotropic variants affect more eGenes in more eTissues, which affect more GWAS traits.

@@

I first analysed whether there are significant differences of some effect consequences between more and less pleiotropic variants.
%
I separated variants according to the count of GWAS categories and computed the EBI variant effect predictor (VEP) consequence \citep{2016.Cunningham.McLaren}.
%
I found a significant larger number of missense variants among variants with 2, 3 and 4 categories compared to variants with 1 category (Fig. \ref{fig:vep_consequence}a).
%
I also found a significant larger number of splicing variants among variants with 3 categories (Fig. \ref{fig:vep_consequence}b).
%
Finally, there is also a larger of the 3'-UTR variants among variants with 4 categories (Fig. \ref{fig:vep_consequence}c).
%
% TODO Discuss sQTLs in 2021.Li.Mu.GenomeBiology.impactcelltype paper
These analyses suggest that more pleiotropic variants have a stronger effect on the coding sequence and splicing regions, which might explain partly their more pleiotropic function.

\subsubsection*{More eGenes per variant-eTissue?}

Then I hypothesized that pleiotropic variants regulate more eGene even when we keep fixed the eTissue.
%
To test this hypothesis, the eGenes per variant-eTissues pairs were counted.
%
Then these eGene counts were classified according to the GWAS category count.
%
If the GWAS category count of a variant changed in different variant-eGene-eTissue trios, then we kept the maximal one.
%
I found means of eGene counts of 1.4, 1.7, 1.7 and 1.6 for GWAS categories counts 5, 4, 3 and 2 compared to eGene count mean of 1.5 for GWAS category count 1 (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
This suggests that pleiotropic variant-eTissue pairs have slightly but significantly (Mann–Whitney U test) more eGenes compared to variants with one GWAS category (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
This observation could be explained by my previous observation that pleiotropic variants have more often an effect on the splicing and 3'UTR regions (Figure \ref{fig:vep_consequence}b,c).

\subsubsection*{More eTissues per variant-eGene?}

My next hypothesis was that pleiotropic variant-eGene pairs are active in more eTissues compared with variant-eGene pairs with one GWAS category and this increases their probability to affect more GWAS categories.
%
To test this hypothesis, the eTissues per variant-eGene pairs were counted.
%
Then these eTissue counts were classified according to the GWAS category count.
%
If the GWAS category count of a variant changed in different variant-eGene-eTissue trios, then we kept the maximal GWAS category count.
%
I found means of eTissue counts of 2.2, 3, 3 and 2.6 for GWAS categories counts 5, 4, 3 and 2 compared to eTissue count mean of 2.5 for GWAS category count 1 (Fig. \ref{fig:gwas_egene_etisue_per_variant}b).
%
This suggests that pleiotropic variant-eGene pairs are active slightly but significantly (Mann–Whitney U test) in more eTissues compared to variants with one GWAS category (Fig. \ref{fig:gwas_egene_etisue_per_variant}b).

\subsubsection*{More GWAS per variant-eGene-eTissue?}

My next hypothesis was that pleiotropic variants are associated to more GWAS categories even after taking into account differences in eGene and eTissue counts.

To test this hypothesis, the GWAS category counts per variant-eGene-eTissue trios were counted.
%
Then these GWAS categorie counts per variant-eGene-eTissue trios were classified according to the GWAS category count per variant.
%
If the GWAS category count per variant changed in different variant-eGene-eTissue trios, then we kept the maximal GWAS category count per variant.
%
I found means of GWAS category counts per variant-eGene-eTissue of 3, 2, 1.6, 1.4 and 1 for GWAS categories counts per variant of 5, 4, 3, 2 and 1 (Fig. \ref{fig:gwas_egene_etisue_per_variant}c).
%
This shows a significant larger number of GWAS categories even in unique trios of variant-eGene-eTissue (Fig. \ref{fig:gwas_egene_etisue_per_variant}c).
%
This observation could be explained by my previous observation that pleiotropic variants have more often missense effects (Fig. \ref{fig:vep_consequence}a).

@@

In Fig. \ref{fig:gwas_egene_etisue_per_variant}b, I observed that pairs of eQTL-eGene are active in more eTissues.
%
To explain this observation, I hypothesized that pleiotropic variants are active in more eTissues, because genomic regions around pleiotropic variants bind more transcription factors, which upregulate the pleiotropic regions in more tissues.
%
To test this hypothesis, I counted the number of unique transcription factors bound in a radius of 50 bp around each variant (Window of 100 bp).
%
I found a significant larger number of transcription factors bound around pleiotropic variants (Fig. \ref{fig:freq_tf_per_variant}a).

Cis-regulatory modules (CRMs) are non-coding genomic regions with a higher density of bound cis-regulatory modules \citep{2021.Ballester.Hammal}.
%
I found that the odds ratio of variants annotated with CRMs vs non-annotated is significantly (Fisher's exact test) higher for variants with 2 and 3 GWAS category counts compared to category count 1 (Fig. \ref{fig:freq_tf_per_variant}b).

\subsection*{How do effect size and }

Pleiotropic variants affect simultaneously more GWAS traits.
%
Therefore it is interesting to investigate how does variant causality and pleiotropy relate to effect size (beta) and significance (p-value) at the level of eQTL and GWAS traits.
%
I found that the mean of the absolute eQTL effect sizes (beta) decreased between GWAS category counts 1 and 5 (Fig. \ref{fig:beta_pval}a).
%
Regarding the eQTL significance (Negative decimal logarithm of the p-values), I found decreasing mean values for GWAS category counts between 1 and 5 (Fig. \ref{fig:beta_pval}b).

Then I carried out the same analysis for the GWAS effect size (beta) and significance (p-value).
%
I found that the mean of the absolute GWAS effect sizes (beta) decreased between GWAS category counts 1 and 5 (Fig. \ref{fig:beta_pval}b).
%
Regarding the GWAS variant significance (Negative decimal logarithm of the p-values), I found increasing mean values for GWAS category counts between 1 and 5 (Fig. \ref{fig:beta_pval}b).

These observations suggest that the strength of both eQTL and GWAS effects decrease with the pleiotropy (Fig. \ref{fig:beta_pval}a,b).

In summary, I observed opposite effects of pleiotropy on the eQTL and GWAS variant strengths.

### 2022-08-28 ms/ms05_floats.tex
ENH intro and discussion
ENH beta and pval improvements

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.66\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_davidgo.py/david_pleio_3.png}
\end{subfigure}

\begin{subfigure}[]{.66\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_davidgo.py/david_pleio_2.png}
\end{subfigure}
%
\caption{Gene ontology analysis of egenes of variants associated to three (\textbf{a}) and two (\textbf{b}) GWAS categories compared to egenes of variants associated to one GWAS category.} \label{fig:geneontology}
\end{figure*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/missense_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/splice_region_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/3_prime_UTR_variant.png}
%
\end{subfigure}
%
\caption{Variant effect predictor (VEP) analysis as a function of the number of GWAS catategory number for three different consequences: \textbf{a}, Missense variant, \textbf{b}, splice region variant and \textbf{c}, 3' UTR variant.} \label{fig:vep_consequence}
%
\end{figure*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_etissue_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_etissue_y_gwas.py/plt.png}
\end{subfigure}
%
\caption{Count of egenes per variant-tissue (\textbf{a}), etissues per variant-egene (\textbf{b}) and GWAS categories per variant-egene-etissue (\textbf{c}).} \label{fig:gwas_egene_etisue_per_variant}
%
\end{figure*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_beta.py/eqtl_beta.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_beta.py/gwas_beta.png}
\end{subfigure}

\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_logpval.py/eqtl.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{d}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_logpval.py/gwas.png}
\end{subfigure}

>>>>

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{0.99\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_davidgo.py/david_pleio_3.png}
\end{subfigure}

\begin{subfigure}[]{.99\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_davidgo.py/david_pleio_2.png}
\end{subfigure}
%
\caption{Gene ontology analysis of egenes of variants associated to three (\textbf{a}) and two (\textbf{b}) GWAS categories compared to egenes of variants associated to one GWAS category.} \label{fig:geneontology}
\end{figure*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/missense_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/splice_region_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/3_prime_UTR_variant.png}
%
\end{subfigure}
%
\caption{Variant effect predictor (VEP) analysis as a function of the number of GWAS catategory number for three different consequences: \textbf{a}, Missense variant, \textbf{b}, splice region variant and \textbf{c}, 3' UTR variant.} \label{fig:vep_consequence}
%
\end{figure*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_etissue_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_etissue_y_gwas.py/plt.png}
\end{subfigure}
%
\caption{Count of egenes per variant-tissue (\textbf{a}), etissues per variant-egene (\textbf{b}) and GWAS categories per variant-egene-etissue (\textbf{c}).} \label{fig:gwas_egene_etisue_per_variant}
%
\end{figure*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_beta.py/eqtl_beta.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_beta.py/gwas_beta.png}
\end{subfigure}

\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_logpval.py/eqtl.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{d}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_logpval.py/gwas.png}
\end{subfigure}
